---
pagetitle: "Nathanael Rolim"
output: 
  pagedown::html_resume:
    self_contained: false
    pdf_mode: true
    css: ['assets/css/resume.css', 'assets/css/overwrite.css']
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
```

Aside
================================================================================

Contact Info {#contact}
--------------------------------------------------------------------------------

```{r, echo=FALSE}
print_contact()
```

Skills {#skills}
--------------------------------------------------------------------------------
I am highly skilled in R, Python (including PySpark), and SQL for robust data analysis. Additionally, I possess a moderate proficiency in Docker for efficient containerization and deployment.

I speak Portuguese (natively), English (Proficiently), French (Intermidiate) and
Spanish (Basic)

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Last updated on `r Sys.Date()`.


Main
================================================================================

Nathanael Rolim {#title}
--------------------------------------------------------------------------------

I hold a degree in International Relations from the University of São Paulo and 
am currently engaged in the field of consumer data and insights. I possess a 
strong analytical focus and aspire to further enhance my technical skills in data 
analysis, particularly with respect to Spark, R, and Python.

I possess a strong team-oriented disposition and firmly believe that collaboration 
constitutes the paramount asset any team can possess in order to surmount the 
challenges of everyday operations.


Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r, echo=FALSE}
print_section("experience")
```


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r, echo=FALSE}
print_section("education")
```


Other Works {data-icon=hands-helping}
--------------------------------------------------------------------------------

```{r, echo=FALSE}
print_section("extra")
```
